Test-driven Knowledge Graph Construction

### 2023-05-06 doc/paper4.tex
Limit upfront axiomatization instead of avoiding it
Shall we acknowledge possible future limitations?

    \item Formalize the terms and relations in a minimum viable ontology using RDF Schema \cite{Brickley2014}. While terms typically map to classes (i.e. instances of \texttt{rdfs:Class}), relations map either to properties (i.e. instances of \texttt{rdf:Property}) or n-ary relations represented by classes. Document the ontology with definitions sourced from and validated by subject-matter experts to create a shared understanding. The ontology should make minimal ontological commitment, so avoid its upfront axiomatization, such as OWL restrictions. The resulting ontology shall serve as an explicit and machine-readable conceptualization of the knowledge graph's domain. Formalizing the ontology may in turn reveal ambiguity in the CQs. Ambiguous CQs cannot be formalized reliably since misinterpretations may occur. In such cases, sources of ambiguity should be revised with subject-matter experts aiming to reformulate the CQs in an unambiguous way.

@@

\section{Limitations}
We are aware of several limitations of the proposed method. Here we recount some of them and suggest how to remedy them. The method may cause the developed artifacts outlined in the Figure \ref{fig:process} to overfit the user requirements in scope, which would hinder the reuse of the artifacts. This shortcoming can be remedied by including more CQs or focusing on reusability during refactoring. User requirements for the knowledge graph under construction can be more complex than what SPARQL can express. One way around it is formalizing the requirements in a more expressive programming language that extends SHACL, such as in \cite{SHACLJS2017}. Ultimately, in order to ameliorate the limitations of this method, it is best combined with other methods, such as those for ontology design (e.g., Kendall and McGuinness \cite{Kendall2019}).

>>>>

    \item Formalize the terms and relations in a minimum viable ontology using RDF Schema \cite{Brickley2014}. While terms typically map to classes (i.e. instances of \texttt{rdfs:Class}), relations map either to properties (i.e. instances of \texttt{rdf:Property}) or n-ary relations represented by classes. Document the ontology with definitions sourced from and validated by subject-matter experts to create a shared understanding. The ontology should make minimal ontological commitment, so limit its upfront axiomatization, such as OWL restrictions. The resulting ontology shall serve as an explicit and machine-readable conceptualization of the knowledge graph's domain. Formalizing the ontology may in turn reveal ambiguity in the CQs. Ambiguous CQs cannot be formalized reliably since misinterpretations may occur. In such cases, sources of ambiguity should be revised with subject-matter experts aiming to reformulate the CQs in an unambiguous way.

@@

\section{Limitations}
We are aware of several limitations of the proposed method. Here we recount some of them and suggest how to remedy them. The method may cause the developed artifacts outlined in the Figure \ref{fig:process} to overfit the user requirements in scope, which would hinder the reuse of the artifacts. This shortcoming can be remedied by including more CQs or focusing on reusability during refactoring. User requirements for the knowledge graph under construction can be more complex than what SPARQL can express. One way around it is formalizing the requirements in a more expressive programming language that extends SHACL, such as in \cite{SHACLJS2017}. Ultimately, in order to ameliorate the limitations of this method, it is best combined with other methods, such as those for ontology design (e.g., Kendall and McGuinness \cite{Kendall2019}). Discovering additional limitations of the method in its future applications in constructing knowledge graph in various settings may help inform and progressively refine the method.
